Choosing harmonies based on average maximum pairwise distance of distributions

### 2020-05-21 algo_rank_harmony.Rmd
updated united table

```{r}
library(readr)
read_rds("data/smart_harmony_wb.rds") %>% knitr::kable()
```

@@

```{r}
read_rds("data/smart_harmony_g.rds") %>% knitr::kable()
```

@@

```{r}
library(readr)
read_rds("data/smart_harmony_norm.rds") %>% knitr::kable()
```

@@

```{r}
read_rds("data/smart_harmony_g.rds") %>% knitr::kable()
```

>>>>

```{r}
library(readr)
smart_weibull <- read_rds("data/smart_harmony_wb.rds")  %>% mutate(rank_weibull = row_number())
```

@@

```{r}
smart_gamma <- read_rds("data/smart_gamma.rds")  %>% mutate(rank_gamma = row_number())
```

@@

```{r}
library(readr)
smart_normal <- read_rds("data/smart_harmony_norm.rds") %>% mutate(rank_normal = row_number())
```

@@

```{r}
smart_general <- read_rds("data/smart_general.rds") %>% mutate(rank_general = row_number())

data_unite <- smart_normal %>% 
  left_join(smart_gamma, by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>%
  rename("MMPD_normal" = "mean_max_variation.x", "MMPD_gamma" = "mean_max_variation.y") %>% 
    left_join(smart_weibull,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>%  rename("MMPD_weibull" = "mean_max_variation") %>% 
  left_join(smart_general,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>%  rename("MMPD_general" = "mean_max_variation") %>% 
  select(-c(facet_levels, x_levels))

data_unite %>% select(-c(MMPD_normal, MMPD_gamma, MMPD_weibull, MMPD_general))
data_unite %>% select(-c(rank_normal, rank_gamma, rank_weibull, rank_general))

```
